Development of User-friendly\\System Identification Techniques

### 2015-10-29 ch02-qlogms/logMS_IMTC.tex
More outline added
Set up glossaries

\section{Introduction} \label{sec:intro}
  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
  Of course, we also want to attain a specified uncertainty level over the full frequency span.

@@

>>>>

\section{Introduction} \label{sec:intro}
  It often occurs that we wish to measure the \gls{FRF} of a \gls{LTI} system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
  Of course, we also want to attain a specified uncertainty level over the full frequency span.

@@

  \begin{table}
  \centering
   \caption{Summary of the different frequency grids.}
    \begin{tabular}{lccc} 
    Grid & Linear & Logarithmic & Quasi-logarithmic \\

    % Limits & \multicolumn{3}{c}{$\ClosedInterval{\fMin, \fMax}$}\\
    Parameters & $f_0, \Delta f$ & $f_0, \alpha$ & $f_0, \Delta f, \alpha$ \\
    $f_{k+1} \isdef$ & $f_{k} + \Delta f$ & $f_{k} \cdot \alpha$ & \ldots \\

    \end{tabular}
    \TODO{afmaken, booktabs}
  \end{table}

### 2015-10-29 front-and-back-matter/frontmatter.tex
Include VC bundle for git/unix
Some formatting
Some small changes
Some TODOs in QLogMS
Use tikz external
Add title page, some bib changes
Set up glossaries

\maketitle

\tableofcontents
%TODO: make sure all these appear in TOC
%TODO: \listoffigures
%TODO: \listoftables
%TODO: list of symbols
%TODO: list of acronyms
\newpage

>>>>

\input{front-and-back-matter/summary.inc.tex}
\input{front-and-back-matter/acknowledgements.inc.tex}

\cleardoublepage
\addcontentsline{toc}{chapter}{Contents}
\tableofcontents
\clearpage

\KOMAoption{listof}{leveldown,totoc}

\listoffigures
\listoftables
% \TOCInsert{section}{List of Listings}   \lstlistoflistings %TODO: fix this

\printglossary[type=\acronymtype,style=long,toctitle={Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,toctitle={List of Symbols}]

\newpage
